On the Origin of Shrimpoluminescence

### 2021-12-07 sonoluminescence/paper/paper.tex
asdsad

\documentclass[prb,aps,11pt,superscriptaddress,floatfix]{revtex4-2} 
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{natmove}
\usepackage{natbib}
\usepackage{hyperref} 
\usepackage{bm}

@@

\title{\huge On the Origin of Shrimpoluminescence}

\author{\large Tyler C. Sterling}
\email{ty.sterling@colorado.edu}
%\affiliation{Department of Physics, University of Colorado at Boulder, Boulder, Colorado 80309, USA}

@@

%\begin{abstract}
%\end{abstract}

@@

\begin{figure}
\includegraphics[width=1\linewidth]{../figs/shrimpy2.pdf}
%    \caption{}
\label{fig:shrimpy}
\end{figure}

@@

\emph{some abbreviations}
\begin{itemize}
    \item SL: sonoluminescence
    \item SBSL: single-bubble sonoluminesence
    \item MBSL: multi-bubble sonoluminescence
    \item EOM: equation(s) of motion
\end{itemize}

\section{rough-outline}
\begin{itemize}
    \item start the introduction with captivating example, i.e. shrimpoluminescence. describe what it is, how it was found, then transition into sonolouminescence. move on to explain how its not understood, various theories try. highlight these. then move on to discuss the experimental situation etc. 
    \item Section: experiment. basically layout what actually is known (by observation) to happen during sonoluminescence. facts only, not trying to explain.
    \item explanations: then move on to theories that try to explain it: thermal, electrical. cover each of these, highlighting thier sucesses and failures.
    \item QED theory: breifly cover this one
\end{itemize}

\section{random notes}
apparently a shitty movie called 'Chain Reaction' with Keanu Reeves was centered around the premise of MBSL as a means of clean energy production. it was based on the speculation that temperatures inside the bubbles ciould reach up to millions of Kelvin and lead to fusion. this was debunked by Prosperetti (see the pop sci article \cite{chainreaction}). He points out that the temp is speculative and is based on assumptions of a perfect sphere collapsing. he notes that its probably not spherical when light is produced and even points out that groups have tried to produce fusion power by intentionally collapsing gas filled micro baloons with lasers... and failed. Tatartcheceko also shows that this is horsehit \cite{tatartchenko2017sonoluminescence}. in this article, Prosperetti also explains how a 'jet' of water whooshing across the bubble could be going faster that 4000 mph, fast enough to cause non-netwownian fracturing of the water leading to light producuction through (apparently) the same mechanism of light emession when ice or wint-o-green mints are snapped in half... huh. this is good introduction fodder. need to find the primary lit.

@@

\section{notes from ref \cite{lohse2018bubble}} 
SBSL was discovered by Giatan et. al. in 1990s at U. Mississippi \cite{gaitan1990experimental,crum1994sonoluminescence,gaitan1992sonoluminescence} (note, \cite{ggaitan1992sonoluminescence} has $\sim$1000 citations..). The SBSL experiments were done by sticking peizoacoustic transducers to the outside of a water filled glass. the 'Bjerknes' force trapps the bubble and the acoustic wave drives its expansion/collapse. What Gaitan saw was that even the single bubble emits light. Wow! This was baffling since 'acoustic energy' \textcolor{red}{(i dont understand this)} is on the order of $\sim10^{-12}$ eV/molecule while visible light is $\sim1$ eV. NVM: I do get this. Typical acoustic waves, e.g. in air, only displace molecules on the order of nanometers, which aquires an elastic energy gaine between molecules of $\sim10^{-12}$ eV/molecule: certainly not enough to excite an electronic transition.

>>>>

\documentclass[rmp,aps,superscriptaddress,floatfix]{revtex4-2} 
\usepackage{graphicx}
\usepackage{xcolor} 
\usepackage{amsmath}
\usepackage{amssymb} 
\usepackage{natmove}
\usepackage{natbib}
\usepackage{hyperref} 
\usepackage{bm}

@@

\title{On the Origin of Shrimpoluminescence}

\author{Tyler C. Sterling}
\email{ty.sterling@colorado.edu}
%\affiliation{Department of Physics, University of Colorado at Boulder, Boulder, Colorado 80309, USA}

@@

\begin{abstract}
shrimpity shrimp shrimp shrimp. abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract abstract 
\end{abstract}

@@

%\emph{Frequently Used Abbreviations}
%\begin{itemize}
%    \item SL: sonoluminescence
%    \item SBSL: single-bubble sonoluminesence
%    \item MBSL: multi-bubble sonoluminescence
%\end{itemize}

\section{Introduction}
Snapping shrimp, like our cute friend in Fig. \ref{fig:shrimp_claw} (left), have long been known to produce cavitating bubbles by \emph{snapping} their claws \cite{versluis2000snapping,lohse2001snapping,tang2019bioinspired}. They have a strong appendage (the \emph{dactyl}) in thier claw [Fig. \ref{fig:shrimp_claw} (center)] that is used to create a very high-velocity jet of water. The low pressure region in the jet's wake forms a bubble [Fig. \ref{fig:shrimp_claw} (t=0 ms)] that, among other things, produces an exceptionally loud noise when it collapses. The sound (i.e. the pressure wave) produced by even a \emph{single} shrimp's snap is detectable over a mile away \cite{everest1948acoustical}. The noise produced by groups of shrimp is so intense that the U.S. Navy used them as ``sonar-camoflauge" in the Pacific ocean during World War II \cite{versluis2000snapping}.

\begin{figure}
\includegraphics[width=0.9\linewidth]{figs/shrimp_claw.pdf}
    \caption{(left) Snapping shrimp (\emph{Alpheus heterochaelis}). (center) Blown-up view of the shrimp's claw. The \emph{plunger} (pl) on the \emph{dactyl} (d) rapidly enters the \emph{socket} (s), ejecting a high-velocity jet of water. The water ejection and subsequent bubble formation and, finally, bubble collape (at t=0) are shown on the right. The units are ms. Adapted from ref. \cite{versluis2000snapping}}
\label{fig:shrimp_claw}
\end{figure}

The shrimp were not patriots helping the war-effort, however; they snapped for food. The shock-wave produced by the cavitating bubble is used to stun and even kill prey \cite{versluis2000snapping}. If the shrimp's prey had very sensitive eyes (and also were not dead) they might notice a flash of light is also produced through an effect referred to as ``shrimpoluminescence" in the case of the pistol shrimp \cite{lohse2001snapping}, but more generally known as \emph{sonoluminescence}.

Sonoluminescence (SL) is more precisely defined as the process by which a ``driven gas bubble collapses so strongly that the energy focusing at collapse leads to light emission" \cite{brenner2002single}. Sonoluminescence comes in two forms: (i) single-bubble sonoluminescence and (ii) multi-bubble sonolumiscence. The disticntion is self-explanatory: multi-bubble sonolumiscence (MBSL) consists of  ``the simultaneous creation and destruction of many seperate, individual cavitation bubbles" \cite{crum1994sonoluminescence,brenner2002single}, whereas in single-bubble sonoluminescence (SBSL), rather obviously, only a single bubble is present \cite{gaitan1992sonoluminescence}. The discovery of MBSL predates SBSL by $\sim$60 years but due to the more-or-less random and fleeting nature of the bubbles, SL in general wasn't well studied until the early 1990's when it was discovered that single bubbles could be created and periodically driven to produce light very high precisions \cite{crum1994sonoluminescence,gaitan1990experimental,gaitan1992sonoluminescence,brenner2002single}. We will discuss MBSL breifly later, but for now it suffices to say that nearly all theoretical and experimental progress has been made using SBSL, with some authors even calling it ``the hydrogen atom of sonoluminescence" \cite{lohse2018bubble,crum1994sonoluminescence}.

The discovery of SBSL created a rush of effort to explain the phenomena with arguments ranging from the simplest models \cite{} to more exotic explanations based of quantum field theory \cite{schwinger1993casimir,eberlein1996sonoluminescence,liberati2000sonoluminescence}.

But besides shrimpoluminescence, why is SL interesting? Well, at a glance, it is not obvious why SL occurs. The acoustic wave in the liquid displaces molecules on the order of nanometers, costing an elastic energy of  $\sim1\times 10^{-12}$ eV/molecule while emitting visible light (through e.g. electronic transitions) costs an energy $\sim1$ eV/molecule \cite{lohse2018bubble,crum1994sonoluminescence}... there is a 12-orders-of-magnitude concentration of energy. That is huge! After a moments thought, however, the massive energy focusing is not that surprising. For example, the energy in the shock wave produced by a cavitating bubble, regardless of the light production, has been known to damage ship propellers since atleast 1917 when Lord Rayleigh's gave the first rigorous treatment of caviating bubbles \cite{gaitan1990experimental}. A heurestic argument goes like this: \cite{plesset1949dynamics}.

So again, why is the light emmission interesting? In short, after 3 decades of studying SBSL, the mechanism of light production is still not understood.

The excitment wasn't restricted to academics however, with SBSL catching Hollywood's attention leading to an unpopular movie called \emph{Chain Reaction} where t

So again, why is the light emmission interesting? After 3 decades of studying SBSL, the physical mechanism of light production in SL is still not understood. This can be seen by glancing at the literature and noticing that there are many recent papers with different arguments for \emph{where} the light comes from \cite{borisenok2020mechanisms,flannigan2013non,flannigan2012temperature,tatartchenko2017sonoluminescence}. We emphasive ``where" since it's not even certain if the light is \emph{surface} or \emph{volumetric} emission, i.e. it is literally not known \emph{where} the light comes from \cite{}.

... and others stating that ``SBSL has become a rather sophisticated testing ground for the ability of mathematical models and numerical simulations to explain detailed experimental data from a complicated physical process" \cite{brenner2002single}.

The goal of this paper is to catch the reader up on recent efforts to explain SBSL. While the author of this paper is particularly excited about shrimpoluminescence, it is important to stress that this work will focus on SBSL in general. It is apparently simpler to create and characterize SBSL in the laboratory without involving shrimp (for example, using shrimp involves convinving them to snap by tickling them \cite{lohse2001snapping,versluis2000snapping,lohse2018bubble}), so practically all work to study SL has not involved shrimp ( ... with notable exceptions \cite{tang2019bioinspired}).

\section{Historical Overview}

\section{What do we know?}
\subsection{The Bubble Wall}
\subsection{Experimental Results}
what conditions are necessary for light emission (i.e. what is the phase space \cite{lohse2018bubble}):
\begin{itemize}
    \item Ar content
    \item driving frequency
    \item P$_{max}$
    \item ...
\end{itemize}

\section{What don't we know}
\subsection{The Bubble Wall (Again)}
\subsection{Experimental Anomalies}

\section{Let there be light!}
\subsection{Thermal Arguments}
\subsection{Electric Arguments}

\subsection{The Casimir Effect}
\subsection{The Casimir Argument}

\section{Summary}

\section{Acknowledgments}

@@

\section{random notes}

argon flash: a method of 'imaging explosions' similar to why argon is more useful for SBSL. argon has no internal DOF whereas air (i.e. N2, O2, water vapor) does and energy from explosions is absorbed dissociating bonds. argon, instead, becomes 'hotter' and emits more light, making photographing explosions easier. see wikipedia article "argon flash"

some dickheads 3d printed a shrimp claw and it also shrimpoluminesces \cite{tang2019bioinspired}

apparently a shitty movie called 'Chain Reaction' with Keanu Reeves was centered around the premise of MBSL as a means of clean energy production. it was based on the speculation that temperatures inside the bubbles ciould reach up to millions of Kelvin and lead to fusion. this was debunked by Prosperetti (see the pop sci article \cite{chainreaction}). He points out that the temp is speculative and is based on assumptions of a perfect sphere collapsing. he notes that its probably not spherical when light is produced and even points out that groups have tried to produce fusion power by intentionally collapsing gas filled micro baloons with lasers... and failed. Tatartcheceko also shows that this is horsehit \cite{tatartchenko2017sonoluminescence}. in this article, Prosperetti also explains how a 'jet' of water whooshing across the bubble could be going faster that 4000 mph, fast enough to cause non-netwownian fracturing of the water leading to light producuction through (apparently) the same mechanism of light emession when ice or wint-o-green mints are snapped in half... huh. this is good introduction fodder. need to find the primary lit.

for fusions, also see wikipedia article on 'bubble fusion' and 'Rusi P Taleyarkhan'. Ruse was some asshole prof at purdue that claimed fusion occured inside cavitating bubbles, but it was later found out that the faked data and interfered with peer reviews leading to him being fucking fired.

@@

\section{notes from ref \cite{lohse2018bubble}} 
SBSL was discovered by Giatan et. al. in 1990s at U. Mississippi \cite{gaitan1990experimental,crum1994sonoluminescence,gaitan1992sonoluminescence} (note, \cite{gaitan1992sonoluminescence} has $\sim$1000 citations..). The SBSL experiments were done by sticking peizoacoustic transducers to the outside of a water filled glass. the 'Bjerknes' force trapps the bubble and the acoustic wave drives its expansion/collapse. What Gaitan saw was that even the single bubble emits light. Wow! This was baffling since 'acoustic energy' \textcolor{red}{(i dont understand this)} is on the order of $\sim10^{-12}$ eV/molecule while visible light is $\sim1$ eV. NVM: I do get this. Typical acoustic waves, e.g. in air, only displace molecules on the order of nanometers, which aquires an elastic energy gaine between molecules of $\sim10^{-12}$ eV/molecule: certainly not enough to excite an electronic transition.
